### 2015-06-08 LOI/COI/COI-lofstead.tex
fixed typo
removed extraneous text

  \item Hasan Abassi, Oak Ridge National Laboratory, collaborator
  \item Andrea Arpaci-Dusseah, UW Madison, co-author
  \item Remzi Arpaci-Dusseau, UW Madison, co-author
  \item Roselyne Barreto, University of Chicago, co-author
  \item John Bent, EMC Corporation, co-author
  \item Michael Booth, Oracle, co-author
  \item Franck Cappello, Argonne National Laboratory, collaborator
  \item Jacqueline Chen, Sandia National Laboratories, co-author
  \item Julian Cummings, California Institute of Technology, co-author
  \item Jai Dayal, Georgia Institute of Technologies, collaborator
  \item Ciprian Docan, Rutgers, co-author
  \item Stephane Ethier, Princenton Univeristy, co-author
  \item Ada Gavrilovska, Georgia Institute of Technology, co-author
  \item Garth Gibson, Carnegie Mellon University, co-author
  \item Ray Grout, National Renewal Energy Laboratory, co-author
  \item Gregory Jean-Baptiste, Florida International University, co-author
  \item Ivo Jimenez, University of California Santa Cruz, co-author
  \item Scott Klasky, Oak Ridge National Laboratory, co-author
  \item Todd Kordenbrock, Hewlett-Packard, collaborator
  \item Seung-Hoe Ku, New York University, co-author
  \item Qing Liu, Oak Ridge National Laboratory, co-author
  \item Mike Lang, Los Alamos National Laboratory, collaborator
  \item Jack Lange, University of Pittsburgh, collaborator
  \item Jeremy Logan, Oak Ridge National Laboratory, co-author
  \item Xiaosong Ma, North Carolina State University, co-author
  \item Carlos Maltzahn, University of California Santa Cruz, collaborator
  \item Kathryn Mohror, Lawrence Livermore National Laboratory, collaborator
  \item Adam Moody, Lawrence Livermore National Laboratory, collaborator
  \item Ron Oldfield, Sandia National Laboratoriey, collaborator
  \item Manish Parashar, Rutgers, co-author
  \item Tom Peterka, Argonne National Laboratory, collaborator
  \item Norbert Podhorzski, Oak Ridge National Laboratory, co-author
  \item Milo Polte, WibiData, co-author
  \item Charles Reiss, University of California Berkeley, co-author
  \item Karsten Schwan, Georgia Institute of Technology, PhD advisor
  \item Arie Shoshani, Lawrence Berkeley National Laboratory, co-author
  \item Alexander Sim, Lawrence Berkeley National Laboratory, co-author
  \item Gregory Sjaardema, Sandia National Laboratories, co-author
  \item Sagar Thapaliya, University of Alabama, Birmingham, collaborator
  \item Yuan Tian, Oak Ridge National Laboratory, co-author
  \item Yandong Wang, Auburn University, co-author
  \item Meghan Wingate McClelland, Xyratex, co-author
  \item Weikuan Yu, Auburn University, co-author
  \item Fang Zheng, IBM, co-author

>>>>

Hasan Abassi, Oak Ridge National Laboratory, collaborator
Andrea Arpaci-Dusseau, UW Madison, co-author
Remzi Arpaci-Dusseau, UW Madison, co-author
Roselyne Barreto, University of Chicago, co-author
John Bent, EMC Corporation, co-author
Michael Booth, Oracle, co-author
Franck Cappello, Argonne National Laboratory, collaborator
Jacqueline Chen, Sandia National Laboratories, co-author
Julian Cummings, California Institute of Technology, co-author
Jai Dayal, Georgia Institute of Technologies, collaborator
Ciprian Docan, Rutgers, co-author
Stephane Ethier, Princenton Univeristy, co-author
Ada Gavrilovska, Georgia Institute of Technology, co-author
Garth Gibson, Carnegie Mellon University, co-author
Ray Grout, National Renewal Energy Laboratory, co-author
Gregory Jean-Baptiste, Florida International University, co-author
Ivo Jimenez, University of California Santa Cruz, co-author
Scott Klasky, Oak Ridge National Laboratory, co-author
Todd Kordenbrock, Hewlett-Packard, collaborator
Seung-Hoe Ku, New York University, co-author
Qing Liu, Oak Ridge National Laboratory, co-author
Mike Lang, Los Alamos National Laboratory, collaborator
Jack Lange, University of Pittsburgh, collaborator
Jeremy Logan, Oak Ridge National Laboratory, co-author
Xiaosong Ma, North Carolina State University, co-author
Carlos Maltzahn, University of California Santa Cruz, collaborator
Kathryn Mohror, Lawrence Livermore National Laboratory, collaborator
Adam Moody, Lawrence Livermore National Laboratory, collaborator
Ron Oldfield, Sandia National Laboratoriey, collaborator
Manish Parashar, Rutgers, co-author
Tom Peterka, Argonne National Laboratory, collaborator
Norbert Podhorzski, Oak Ridge National Laboratory, co-author
Milo Polte, WibiData, co-author
Charles Reiss, University of California Berkeley, co-author
Karsten Schwan, Georgia Institute of Technology, PhD advisor
Arie Shoshani, Lawrence Berkeley National Laboratory, co-author
Alexander Sim, Lawrence Berkeley National Laboratory, co-author
Gregory Sjaardema, Sandia National Laboratories, co-author
Sagar Thapaliya, University of Alabama, Birmingham, collaborator
Yuan Tian, Oak Ridge National Laboratory, co-author
Yandong Wang, Auburn University, co-author
Meghan Wingate McClelland, Xyratex, co-author
Weikuan Yu, Auburn University, co-author
Fang Zheng, IBM, co-author
